Lab 2 Final Report: COVID-19 Case Rate vs Population Demographics and Mask Policy

### 2020-12-06 Jackson_Liu_Temlock_Zhang_Lab2_Draft_Report.Rmd
Updated CLM section.

In examining the results of various diagnostics across different models, generally the CLM assumptions are best met with the second model. In the first model, deviations away from certains assumptions are the strongest. This is seen mostly with regards to the linear conditional expectation assumption, where the residuals against the fitted values have a noticeable inverted "V" shape as opposed to being constant around zero. In the second model, the same diagnostic shows that the assumption is better met.

However, when adding more variables in the third model, other assumptions begin to be less well met. For example, the normality of the error term in the model is less well fit than it was in the earlier models. It can be seen in the QQ plot for the model how at fitted values towards the edges of the model's range, the is the greatest deviation away from normality. This assumption is generally less important than that of the linear conditional expectation, however, where the latter is a fundamental part of CLM.

>>>>

In examining the results of various diagnostics across different models, generally the CLM assumptions are better met as the model continues to develop. In the first model, deviations away from certain assumptions are the strongest. This is seen mostly with regards to the linear conditional expectation assumption, where the residuals against the fitted values have a noticeable inverted "V" shape as opposed to being constant around zero. In the second model, the same diagnostic shows that the assumption is better met. This is further improved upon in the third model, where local variations in the linear conditional expectation diagnostic plot are generally smoother and more centered around zero. The assumption with the greatest exception to this is that of no high colinearity within the models, as each coefficient in each model was shown to have VIF values not near the cut off value of four.

However, when adding more variables in the third model, other assumptions begin to be less well met. For example, the normality of the error term in the model is less well fit than it was in the earlier models. It can be seen in the third model's Q-Q plot how at fitted values towards the edges of the model's range, there exists the greatest deviation away from normality. This assumption is generally less important than that of the linear conditional expectation, however, which is a fundamental part of CLM. Therefore, the third model can still be considered as generally improving the overall analysis.

In addition, with more variables in the third model, outliers appear to have more of an impact than previously. This is likely due to the limited number of data points the model is based off of, an entire state only constitutes an individual datapoint. With less degrees of freedom in the third model, certain points can be seen to more closely approach the boundaries of the Cook's length plot, although they are still not extreme enough to fully be considered an outlier. Increasing the resolution of the data, such as examining COVID-19 cases at the county or city/town level, would help to reduce this by increasing the overall degrees of freedom.
